%======================== Copyright
\thispagestyle{empty}
\setcounter{page}{1}
\vspace*{\fill}

\textbf{\thesistitle} \newline
\thesissubtitle

\smallskip

%\documenttype \newline
%\thedate

\smallskip

By \newline
(\studentnumber) \thesisauthor

\bigskip

\textbf{Advisor(s)}\newline
\ThSupervisors

\vspace{3cm}

\begin{tabularx}{\textwidth}{@{}lX@{}}
    Education     & \documenttype                                                                                                                                            \\
    Programme     & \programme\\[4mm]
    Period        & \projectperiod\\[4mm]
    ECTS          & \thesissize \\[4mm]
    Copyright:    & \thesisauthor \, \thesisyear \\[2mm]
    & Reproduction of this publication in whole or in part must include the customary bibliographic citation, including author attribution, report title, etc. \\[9mm]
    Cover photo:  & \thesisauthor, 2025 \\[4mm] % yellow leafs
    Published by: & DTU, \departmentdescriber,                                                                                                                               \\
    & \addressI, \addressII ~Denmark                                                                                                                           \\
    & \url{\departmentwebsite} \\[4mm]
    Remark        & This report is submitted as partial fulfillment of the requirements for graduation in the above education at the Technical University of Denmark.\\[9mm]

% for phd thesis only
%    ISSN: & [0000-0000] (electronic version) \\
%    ISBN: & [000-00-0000-000-0] (electronic version) \\
%    & \\
%    ISSN: & [0000-0000] (printed version) \\
%    ISBN: & [000-00-0000-000-0] (printed version)
\end{tabularx}


%======================== Abstract
\clearpage
\pagestyle{main}
\section*{Abstract}\label{sec:abstract}
\addcontentsline{toc}{section}{Abstract}

%{\textcolor{dtured}{An abstract is a bit from the introduction, a bit about the work done and the main conclusion.}}

\thesisabstract

%======================== Acknowledgements
\clearpage
\section*{Acknowledgements}\label{sec:acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

I would like to express my gratitude to my supervisor, Søren Hansen, for the trust he put in me and for allowing me to conduct my master’s thesis abroad in France.
The topic I was offered aligned perfectly with my interests, and it was a great opportunity to work on it.

I extend special thanks to Alexandre Chapoutot and Thibault Toralba, who thought of me for this subject.
I am grateful for their guidance and the trust they placed in me and my intuitions.

I also wish to thank Clément, Adrien, David, Rémi, Joris, and Danil,
with whom I had the pleasure of working, sharing problems, and finding solutions.

During my work, I used the dataset from~\citetitle{fortin_uav-assisted_2024} very kindly provided by Jean-Michel Fortin of the Northern Robotics Laboratory.
I am sincerely grateful to him for providing access to the dataset.

Finally, the overwhelming majority my thesis' work is open source and available on \href{https://github.com/Seb-sti1/mastersthesis}{my github}.