\chapter{Context}

This master's thesis took place at the U2IS, the computer science lab of ENSTA Paris.
The lab has some robots and sensors with each of them having their particularities.

Also, while I was working at the lab, my team was participating in a robotics challenge named CoHoMa.
This challenge aims at making a fleet of UAV and UGV move and recognize red boxes on an unstructured terrain.


\section{Robots}

The primary \gls{ugv}s in the lab are currently two \href{https://www.shark-robotics.com/robots/barakuda-mule-robot}{Barakuda from SharkRobotics}
and the main \gls{uav}s are two \href{https://www.hexadrone.fr/produits/drone-tundra/}{Tundra 1 from hexadrone}.
Before acquiring the Barakuda robots, the lab used several
\href{https://clearpathrobotics.com/husky-a300-unmanned-ground-vehicle-robot/}{Husky from Clearpath Robotics} for
outdoors robotics experiments.

\subsection{Barakuda}

% TODO add pictures of barakuda, tundra, husky

Multiple sensors have been integrated onto the Barakuda robots to enhance their perception capabilities.
Among them, two main cameras have been installed: the \href{https://www.stereolabs.com/en-fr/products/zed-2}{ZED 2i} stereo RGB-D camera and the \href{https://www.axis.com/products/axis-q62-series}{AXIS Q62 PTZ} camera.
The ZED 2i is mounted at the front of the robot and is used to capture RGB-D images of the immediate environment, providing depth information for navigation and mapping tasks.
The AXIS Q62 PTZ camera is mounted on a mast approximately XX cm above the robot's center and can be remotely controlled along the pitch and yaw axes, enabling wide-area visual coverage. % TODO fill the height of the PTZ
This is particularly useful during teleoperation, as it provides the operator with improved awareness of the \gls{ugv}'s footprint relative to its environment.
In addition to the two cameras, a \gls{lidar} sensor is mounted at the front of each robot: one Barakuda is equipped with an \href{https://ouster.com/products/hardware/osdome-lidar-sensor}{OSDome}, while the other uses an \href{https://ouster.com/products/hardware/os1-lidar-sensor}{OS1}.
All sensors are connected to an NVIDIA Jetson AGX Orin.

% TODO add schematics of barakuda
% TODO add jetson spec in appendix?

Docker containers running ROS Noetic are deployed on the Jetson.
These containers are used to manage the software environment, which can be challenging to configure directly on the Jetson, particularly for library dependencies.
Within the containers, ROS Noetic nodes handle sensing, data processing, and interaction with commands and the environment.

\subsection{Tundra}

tundra drone with gimbal and jetson

\subsection{Husky}

\subsection{Wireless connection, teleoperation, monitoring}

detailed explanation of the robots: sensors, software, how then interact


\section{Perception and autonomous capabilities}


\section{CoHoMa}

current challenges/direction of the lab
