\section*{Abstract}\label{sec:abstract}
\addcontentsline{toc}{section}{Abstract}

This project explores the collaboration between an aerial drone and a terrestrial robot for navigating unstructured environments.
The drone performs initial environmental mapping using sensors (e.g.\ GNSS, cameras\ldots), generating a topological map with identified paths, intersections, and potential targets.
The terrestrial robot receives high-level instructions (e.g., “reach a target”) and navigate using this topological map.
It utilizes onboard sensors to match environmental features previously detected with the drone and associated to the topological map.

\vspace{5cm}

\section*{Acknowledgements}\label{sec:acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

I would like to express my gratitude to my supervisor, Søren Hansen, for allowing me to conduct my master’s thesis abroad in France.
The topic I was offered aligned perfectly with my interests, and it was a great opportunity to work on it.

I extend special thanks to Alexandre Chapoutot and Thibault Toralba, who thought of me for this subject.
I am grateful for their guidance and the trust they placed in me and my intuitions.

I also wish to thank Clément Yver, Adrien Poiré, David Filliat, Rémi Marsal, Joris Tillet, and Danil Berrah,
with whom I had the pleasure of working, sharing problems, and finding solutions.

During my work, I used the publicly available~\cite{noauthor_aukerman_nodate} and the one used in
~\cite{fortin_uav-assisted_2024} very kindly provided by Jean-Michel Fortin of the Northern Robotics Laboratory.
I am very grateful that I could use them and thank the authors.

Finally, the overwhelming majority my thesis' work is available on \href{https://github.com/Seb-sti1/mastersthesis}{my github}.